\documentclass[12pt,a4paper]{caspset}
% set 1-inch margins in the document
\usepackage[left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{courier}
\usepackage{multimedia}
\usepackage[toc,page,title,titletoc,header]{appendix}
\usepackage{color, soul}
\usepackage{wrapfig}
%\usepackage{Picinpar}
\usepackage{xypic}
\setulcolor{red}

\newcommand{\hmwkTitle}{English writing}
\newcommand{\hmwkSubTitle}{My Hometown} % No subtitle, so this will be excluded
\newcommand{\hmwkDueDate}{\today}
\newcommand{\hmwkClass}{College of English}
\newcommand{\hmwkClassTime}{Thu.{~}08:00}
\newcommand{\hmwkClassInstructor}{Philip Dykshoorn}
\newcommand{\hmwkAuthorName}{Zhou Lvwen}


%% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClassInstructor\ ~\ \hmwkClassTime: \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \protect\pageref{LastPage}}            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\picwidth
\setlength\picwidth{0.23\textwidth}
\newlength\pichigh
\setlength\pichigh{1.277\picwidth}

% info for header block in upper right hand corner
\name{Zhou Lvwen{~}201128000718065}
\class{Class B-165}
\assignment{Assignment \# 02}
\duedate{March 7, 2013}
\setlength{\parskip}{1.2em}
\setlength\parindent{0pt}
\linespread{1.3}
\begin{document}

\problemlist{\large A Person that I Admire}
There are a lot of people that I admire. I admired my father when I was a young boy. I admired math teacher when I was a high school student. In this essay, I want to write about somebody that I have known in my college days. I graduated from high school and went to study physics in the university in 2006. When I was just starting my second year at university, I joined mathematical modeling studio (An association of our university) and recognized some mathematical model fans, and He Wei is one of them.

He Wei comes from Zhejiang province. He was of middle height and slightly overweight for a southerner. He had short hair with a natural recreational hair style, which look a little disorder. He has clear face with a pair of small eyes. His teeth were black due to smoking. He talks culturedly and has a deep impression on me.

He seems careless about his clothes. He used to slop around all day in regular black jacket and old dark blue jeans. His shoes are dark and his socks are brown. Obviously his white shoes did not match his dark color jacket and jeans. Through a conversation with him, I found he was outgoing and easy to get along with.

I admired He Wei because he was good at mathematical modeling. For a complex practical problem, he always can refine it, phrase it in mathematical terms, and then reverse the process, translate the mathematical solution back into a comprehensible. We worked together several times and solved some problems.

I went to his wedding last year and heard that he turned businessman. It is a pity that he gave up mathematics.
\end{document}
