\documentclass[12pt,a4paper]{caspset}
% set 1-inch margins in the document
\usepackage[left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{courier}
\usepackage{multimedia}
\usepackage[toc,page,title,titletoc,header]{appendix}
\usepackage{color, soul}
\usepackage{wrapfig}
%\usepackage{Picinpar}
\usepackage{xypic}
\setulcolor{red}

\newcommand{\hmwkTitle}{English writing}
\newcommand{\hmwkSubTitle}{My Hometown} % No subtitle, so this will be excluded
\newcommand{\hmwkDueDate}{\today}
\newcommand{\hmwkClass}{College of English}
\newcommand{\hmwkClassTime}{Thu.{~}08:00}
\newcommand{\hmwkClassInstructor}{Philip Dykshoorn}
\newcommand{\hmwkAuthorName}{Zhou Lvwen}


%% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClassInstructor\ ~\ \hmwkClassTime: \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \protect\pageref{LastPage}}            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\picwidth
\setlength\picwidth{0.23\textwidth}
\newlength\pichigh
\setlength\pichigh{1.277\picwidth}

% info for header block in upper right hand corner
\name{Zhou Lvwen{~}201128000718065}
\class{Class B-165}
\assignment{Assignment \# 07}
\duedate{April 19, 2013}
\setlength{\parskip}{1.2em}
\setlength\parindent{0pt}
\linespread{1.3}
\begin{document}

\problemlist{\large The white piano}

My girlfriend is able to play the piano. Since I known my girlfriend, she dreamed of having a piano. There is a white piano in the shopping plaza where we use to always go. Whenever we were shopping in the plaza, she always could not stop herself from looking at the piano. Sometimes she even played the piano for a while.

One day last summer, my girlfriend and I rambled together in the shopping plaza. When we were passing the piano, she stopped with a wistful facial expression.

``Would you buy me a white piano?'' she asked and pointed to the piano beside her,``Just like this one''.\\
``Well, when you are 25 years old, I will buy you one''.\\
``Really?'' She looked at me very excited, ``just two months, I will be 25.''\\
``Of course,'' Said I paused, ''But in my heart, you will always 18 years old.''\\
``You are a disgusting liar,'' An odd grimace crosses her mouth and the excited expression vanishes.

Two months later, on my girlfriend’s birthday. My girlfriend and I ate at a restaurant.

``I'll give you a big surprise, a big, really big...'' I said ``do you remember the white piano?''\\
``Oh, what a pleasant surprise!,'' she was so happy that squealed, ``Where is my white piano?''\\
``I brought you a toothbrush with the same color as the piano,...''

In March of this year, I really bought her a white electric piano.

\end{document}
