\documentclass[12pt,a4paper]{caspset}
% set 1-inch margins in the document
\usepackage[left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{courier}
\usepackage{multimedia}
\usepackage[toc,page,title,titletoc,header]{appendix}
\usepackage{color, soul}
\usepackage{wrapfig}
%\usepackage{Picinpar}
\usepackage{xypic}
\setulcolor{red}

\newcommand{\hmwkTitle}{English writing}
\newcommand{\hmwkSubTitle}{My Hometown} % No subtitle, so this will be excluded
\newcommand{\hmwkDueDate}{\today}
\newcommand{\hmwkClass}{College of English}
\newcommand{\hmwkClassTime}{Thu.{~}08:00}
\newcommand{\hmwkClassInstructor}{Philip Dykshoorn}
\newcommand{\hmwkAuthorName}{Zhou Lvwen}


%% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClassInstructor\ ~\ \hmwkClassTime: \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \protect\pageref{LastPage}}            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\picwidth
\setlength\picwidth{0.23\textwidth}
\newlength\pichigh
\setlength\pichigh{1.277\picwidth}

% info for header block in upper right hand corner
\name{Zhou Lvwen{~}201128000718065}
\class{Class B-165}
\assignment{Assignment \# 10}
\duedate{May 9, 2013}
\setlength{\parskip}{1.2em}
\setlength\parindent{0pt}
\linespread{1.3}
\begin{document}
\vspace{-28pt}
\problemlist{\large Cover Letter for Application for Employment}
\vspace{-10pt}
Dr. Alex Twist, President\\
Sugar Corporation\\
No.15 Beisihuanxi Road\\
Beijing, China 100190

Dear Dr. Twist, \hspace{265pt} May 10, 2013

This letter is in reply to your advertisement on \underline{job.com} on May 1, 2013, calling for a mechanical engineer with a background rich in computational fluid mechanics.

I graduated from Dalian University with a B.S. in physics in 2010. From 2010 to the present day, I am doing my master's degree in the Institute of Mechanics, Chinese Academy of Sciences. I will receive my master's degree in early July 2014, under the supervision of Dr. M.B. Liu. My studies have included courses in computational fluid mechanics and numerical simulations, and I have simulated many phenomena of flow in micro-channels.

I have published four papers until now, one of them were published in \underline{Physical} \underline{Review E}. In addition, my another research paper was accepted by \underline{Physics} \underline{of Fluids}, and it will be publish in September 2013. 

I am proficient in fluid mechanics and numerical simulation methods.  I am familiar with many programming languages(such as C/C++, Python and LaTex) and multiple platforms(such ans Windows, Linux and Unix). 

With my educational background and working experience, I believe I am qualified for the job.  I hope to hear from you as soon as possible. Thank you.

Yours sincerely,
\\
\\

Zhou Lvwen

\end{document}
