\documentclass[12pt,a4paper]{caspset}
% set 1-inch margins in the document
\usepackage[left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{courier}
\usepackage{multimedia}
\usepackage[toc,page,title,titletoc,header]{appendix}
\usepackage{color, soul}
\usepackage{wrapfig}
%\usepackage{Picinpar}
\usepackage{xypic}
\setulcolor{red}

\newcommand{\hmwkTitle}{English writing}
\newcommand{\hmwkSubTitle}{My Hometown} % No subtitle, so this will be excluded
\newcommand{\hmwkDueDate}{\today}
\newcommand{\hmwkClass}{College of English}
\newcommand{\hmwkClassTime}{Thu.{~}08:00}
\newcommand{\hmwkClassInstructor}{Philip Dykshoorn}
\newcommand{\hmwkAuthorName}{Zhou Lvwen}


%% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClassInstructor\ ~\ \hmwkClassTime: \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \protect\pageref{LastPage}}            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\picwidth
\setlength\picwidth{0.23\textwidth}
\newlength\pichigh
\setlength\pichigh{1.277\picwidth}

% info for header block in upper right hand corner
\name{Zhou Lvwen{~}201128000718065}
\class{Class B-165}
\assignment{Assignment \# 01}
\duedate{February 28, 2013}
\setlength{\parskip}{1.2em}
\setlength\parindent{0pt}
\linespread{1.5}
\begin{document}

\problemlist{\large My Hometown}

My hometown is Yangzhou, which is located in central Jiangsu province, sitting on the northern bank of the Yangtze River and approximately 200km southwest of Shanghai. Yangzhou, still known as Guangling, are comprised of about 4,000,000 people and 2000 $km^2$ area.

Yangzhou is a historical and cultural city. It was founded more than 2500 years ago. Historically it is one of the wealthiest of China's cities, known at various periods for its great merchant families, poets, painters, scholars and politicians. Such as Bai juyi, one of the most famous poets in Tang Dynasty, has lived in Yangzhou for a few years; Jiang zemin, the former president of China, is a people of Yangzhou; Even Wei Xiaobao, the famous character of Jin Yong’s book, is also come from Yangzhou. 

Yangzhou is a beatuful and Livable city. The impression of the whole city is just like jasmine, small but exquisite. What's more, in summer, the whole city is filled with fragrance of jasmine. Life in Yangzhou is very comfortable. The city is creating an exquisite kind of life under the concept of "being humane, ecological and livable". Yangzhou is also famous for beautiful woman. It is said that climate conditions in Yang zhou is of great benefit to female appearance, although it is not supported by scientific evidence.

Although I have left Yangzhou for more than 5 years. As an people of Yangzhou, I love Yangzhou for its history, culture, fragrance and people. 
\end{document} 
