\documentclass[12pt,a4paper]{caspset}
% set 1-inch margins in the document
\usepackage[left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{courier}
\usepackage{multimedia}
\usepackage[toc,page,title,titletoc,header]{appendix}
\usepackage{color, soul}
\usepackage{wrapfig}
%\usepackage{Picinpar}
\usepackage{xypic}
\setulcolor{red}

\newcommand{\hmwkTitle}{English writing}
\newcommand{\hmwkSubTitle}{My Hometown} % No subtitle, so this will be excluded
\newcommand{\hmwkDueDate}{\today}
\newcommand{\hmwkClass}{College of English}
\newcommand{\hmwkClassTime}{Thu.{~}08:00}
\newcommand{\hmwkClassInstructor}{Philip Dykshoorn}
\newcommand{\hmwkAuthorName}{Zhou Lvwen}


%% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClassInstructor\ ~\ \hmwkClassTime: \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \protect\pageref{LastPage}}            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\picwidth
\setlength\picwidth{0.23\textwidth}
\newlength\pichigh
\setlength\pichigh{1.277\picwidth}

% info for header block in upper right hand corner
\name{Zhou Lvwen{~}201128000718065}
\class{Class B-165}
\assignment{Assignment \# 03}
\duedate{March 14, 2013}
\setlength{\parskip}{1.2em}
\setlength\parindent{0pt}
\linespread{1.3}
\begin{document}

\problemlist{\large A Memorable Event}

Time flies, and twenty years is just a blink of an eye. With the passage of time, many events were forgotten, but some are in remembrance just like happened yesterday. In this essay, I will describe something that happened in my high school days. I was in high school from 2004 to 2006. Like most students, ordinarily I sleep in dormitory provided and attend the same school, and goes home only on the last two days of a moth.

It was a cold winter morning in 2005, a year before I finished high school, I got up at six that morning as usual. After brushing teeth, Zhang Mong, one of my roommates, and I just come out of the dormitory and want to go to the classroom. At that time, a student slipped and fell down a flights of stairs. His head charged into a doorpost and hurt. He stood up, and then his fingers splayed out in front of him, his mouth working heaved and fell again. The wound was bleeding freely. We quickly raised him, but he lost consciousness with the continued loss of blood. Zhang Mong and I were covered in blood. I suddenly felt that life is so fragile. We have to call for more people and an ambulance. At last, he was brought to the hospital. 

After this, I feel really depressed for a few days, and thought about life and death. I still remember his face although I have not seen him since then. I am even doubtful whether he is still alive. Life is so fragile, we should cherish this moment for we unable to predict the potential fatal disaster in next moment.


\end{document}
