\documentclass[12pt,a4paper]{caspset}
% set 1-inch margins in the document
\usepackage[left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{courier}
\usepackage{multimedia}
\usepackage[toc,page,title,titletoc,header]{appendix}
\usepackage{color, soul}
\usepackage{wrapfig}
%\usepackage{Picinpar}
\usepackage{xypic}
\setulcolor{red}

\newcommand{\hmwkTitle}{English writing}
\newcommand{\hmwkSubTitle}{My Hometown} % No subtitle, so this will be excluded
\newcommand{\hmwkDueDate}{\today}
\newcommand{\hmwkClass}{College of English}
\newcommand{\hmwkClassTime}{Thu.{~}08:00}
\newcommand{\hmwkClassInstructor}{Philip Dykshoorn}
\newcommand{\hmwkAuthorName}{Zhou Lvwen}


%% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClassInstructor\ ~\ \hmwkClassTime: \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \protect\pageref{LastPage}}            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\picwidth
\setlength\picwidth{0.23\textwidth}
\newlength\pichigh
\setlength\pichigh{1.277\picwidth}

% info for header block in upper right hand corner
\name{Zhou Lvwen{~}201128000718065}
\class{Class B-165}
\assignment{Assignment \# 03}
\duedate{March 21, 2013}
\setlength{\parskip}{1.2em}
\setlength\parindent{0pt}
\linespread{1.3}
\begin{document}

\problemlist{\large A Strange Happening}

I almost have never had any problem with night and I am not afraid of the dark. When I was in my hometown, I frequently ride an electric bike on the road from the town to my home in the night. I have to pass a piece of farmland on my way to home. The farmland is a desolate place. It is said the farmland was an abandon graveyard before. But a strange thing that happened in a night Last year had left me rather shaky.

It was a winter night last year. I ride electric bike on my way to home as usual. The night was dark and I can only see things that illuminated by the headlight of my e-bike. When I passed the farmland, I saw a quaint old lady, who wore a dark cape, walking on the right side of the front road. The headlight of my e-bike illuminated her face when she turns to look at me. Her face conveyed an unmistakably brittle air. I passed her too fast to see her face clearly. Just when I was curious about why an old lady walks on the road alone in such a dark night, there was another old lady in the front. Just like the lady before, she wore the same cape. She turned to look at me in the same way. And I saw the same face. I was almost certain that they were the same one. I became very frightened and ride electric bike at the highest speed. Fortunately, I had arrived at home safely.

Although it happened in flash and passed one year, in retrospect it made my hair stand on end.  And I still haven't figured that out yet.


\end{document}
