\documentclass[12pt,a4paper]{caspset}
% set 1-inch margins in the document
\usepackage[left=3.18cm,right=3.18cm,top=2.54cm,bottom=2.54cm]{geometry}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{extramarks}
\usepackage{chngpage}
\usepackage{soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{graphicx,float,wrapfig}
\usepackage{ifthen}
\usepackage{listings}
\usepackage{courier}
\usepackage{multimedia}
\usepackage[toc,page,title,titletoc,header]{appendix}
\usepackage{color, soul}
\usepackage{wrapfig}
%\usepackage{Picinpar}
\usepackage{xypic}
\setulcolor{red}

\newcommand{\hmwkTitle}{English writing}
\newcommand{\hmwkSubTitle}{My Hometown} % No subtitle, so this will be excluded
\newcommand{\hmwkDueDate}{\today}
\newcommand{\hmwkClass}{College of English}
\newcommand{\hmwkClassTime}{Thu.{~}08:00}
\newcommand{\hmwkClassInstructor}{Philip Dykshoorn}
\newcommand{\hmwkAuthorName}{Zhou Lvwen}


%% Setup the header and footer
\pagestyle{fancy}                                                       %
\lhead{\hmwkAuthorName}                                                 %
\chead{\hmwkClassInstructor\ ~\ \hmwkClassTime: \hmwkTitle}  %
\rhead{Page\ \thepage\ of\ \protect\pageref{LastPage}}            %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newlength\picwidth
\setlength\picwidth{0.23\textwidth}
\newlength\pichigh
\setlength\pichigh{1.277\picwidth}

% info for header block in upper right hand corner
\name{Zhou Lvwen{~}201128000718065}
\class{Class B-165}
\assignment{Assignment \# 05}
\duedate{March 28, 2013}
\setlength{\parskip}{1.2em}
\setlength\parindent{0pt}
\linespread{1.3}
\begin{document}

\problemlist{\large A embarrass thing}

In the summer of my fourth year in the university, my classmates and I often have dinner together. We also drink some beer or wine with dinner. There are several restaurants across from our university. A restaurant frequented by us was of two stories.  The two floors were connected with each other by a narrow wooden stairway. 

One day, my roommate and I, and all other classmates have dinner together in the restaurant as usual. We drew around a table in a private room on the second floor. We eating, drinking wine and talking. My roommate, whose name is Yang, had no tolerance for alcohol, and in the end fell down dead drunk. After the dinner, I and another classmate help Yang down steps. Right before we reach the first floor, Yang throw up his food, and left a large piece of vomit. But that's not the worst part. The vomit made the narrow passageway slippery. A student, whose name is Zhang, just behind me stepped on the vomit,  slipped and fall on the vomit. Zhang covered from head to foot with vomit. This did not raise a smile in that instant, which was embarrassing. In this really embarrassing situation, but Zhang managed to laugh it off after a few seconds. Zhang laughed, and then we all laughed too.


Although I graduated from university for two years, I still take delight in talking about the embarrassing story when meet the old classmates.


\end{document}
